### 2023-09-13 thesis/MSECE_thesis.tex
Add outlier trimmed data table. Fix bug in remove outlier function.

>>>>

The corpora statistics after outlier removal are presented in Table \ref{tab:corpora_stats_outlier_removed}, below.

\begin{table}[h!]
    \centering
    \begin{tabular}{l r r r r}
        \toprule
        \textbf{Corpus} & \textbf{Samples} & \textbf{Mean Sequence Length (\(\pm \sigma\))} & \textbf{Unique Tokens} & \textbf{Tokens} \\
        \midrule
        ATCC            & 28,335           & \(10.81 \pm 5.43\)                             & 2,006                  & 306,382         \\
        ATCO2           & 848              & \(11.91 \pm 5.07\)                             & 812                    & 10,103          \\
        ATCOSIM         & 9,438            & \(11.13 \pm 3.86\)                             & 787                    & 105,017         \\
        ZCU CZ ATC      & 14,275           & \(9.87 \pm 5.24\)                              & 2,967                  & 140,855         \\
        \midrule
        Total           & 52,896           & \(10.63 \pm 5.15\)                             & 4,884                  & 562,357         \\
        \bottomrule
    \end{tabular}
    \label{tab:corpora_stats_outlier_removed}
    \caption{Individual and cumulative corpora statistics after outlier removal.}
\end{table}
